### 2017-08-30 paper/evaluation.tex
Removed outdated comment
Moved content about flaky tests from intro to sec III

From these \SubjectsGithub{} downloaded projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory and \SubjectsGithubNotTestable{}
projects were unable to test due to incompatible environment (\eg,
missing required web browser or database management system).
In addition, we identified \SubjectsGithubFlaky{} projects with flaky
tests.
As some of our experiments consist in running tests in a multithreaded
configuration, we ignored these projects as it would be impractical
for us to identify whether a test failed due to a race condition.
Our final set of subjects consists of \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

@@

We took the following actions to isolate our environment from
measurement noise.  First, we observed that some test tasks called
test-unrelated tasks (\eg, \emph{javadoc} generation and static
analyses) that could interfere in our time measurements.  To address
that potential issue, we inspected Maven execution logs from a sample
including a hundred projects prior to running the script from
Figure~\ref{fig:mvn-execution}.  The tasks we found were ignored from
execution (lines 1-4).  Furthermore, to avoid noise from operating
system events, we configured our workstation to run only essential
services.  The machine was dedicated to our experiments and we
accessed it via SSH. In addition, we configured the \CodeIn{isolcpus}
option from the Linux Kernel \cite{linux-kernel} to isolate six
virtual CPUs to run our experiments, leaving the remaining CPUs to run
OS processes~\cite{isolcpus-use}.  The rationale for this decision is
to prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared timings corresponding to the
sequential execution of tests using Maven with that obtained with
JUnit's default \CodeIn{JUnitCore} runner, invoked from the command
line.  Results were very close.
\Jbc{This is not true for projects running tests in parallel by defaut.
Recall from RQ3 that some projects run tests in parallel by default.
How should we address this?}

>>>>

From these \SubjectsGithub{} downloaded projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory and \SubjectsGithubNotTestable{}
projects were unable to test due to incompatible environment (\eg,
missing required web browser or database management system).
In addition, we identified \SubjectsGithubFlaky{} projects with
non-deterministic test results.
In general, a test that either pass or fail under the same circumstances
is known as a ``flaky test''~\cite{luo-etal-fse2014}.
\Comment{While there are several causes that may introduce randomness on test
results, our concern is on flakiness caused by
parallel execution.}
As some of our experiments consist in running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
Our final set of subjects consists of \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

@@

We took the following actions to isolate our environment from
measurement noise.  First, we observed that some test tasks called
test-unrelated tasks (\eg, \emph{javadoc} generation and static
analyses) that could interfere in our time measurements.  To address
that potential issue, we inspected Maven execution logs from a sample
including a hundred projects prior to running the script from
Figure~\ref{fig:mvn-execution}.  The tasks we found were ignored from
execution (lines 1-4).  Furthermore, to avoid noise from operating
system events, we configured our workstation to run only essential
services.  The machine was dedicated to our experiments and we
accessed it via SSH. In addition, we configured the \CodeIn{isolcpus}
option from the Linux Kernel \cite{linux-kernel} to isolate six
virtual CPUs to run our experiments, leaving the remaining CPUs to run
OS processes~\cite{isolcpus-use}.  The rationale for this decision is
to prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared timings corresponding to the
sequential execution of tests using Maven with that obtained with
JUnit's default \CodeIn{JUnitCore} runner, invoked from the command
line.  Results were very close.

### 2017-08-30 paper/related.tex
Moved content about flaky tests from intro to sec III

\textbf{Usage of massively parallel hardware:}
Previous research investigated the feasibility of testing embedded
software on \emph{Graphics Processing Units} (GPUs) as an alternative
to multicore CPUs~\cite{rajan-etal-ase2014}.
The \emph{Simple Instruction Multiple Data} (SIMD) architecture of
modern GPUs allows to run the same test case with different test data
over several threads.
Although benchmarks indicate far superior performance over traditional
multicore CPUs, existing GPU programming-models (\eg,
CUDA~\cite{cuda}, and OpenCL~\cite{opencl}) are compatible only with a
subset of the C/C++ language.
Recent work proposed a compiler-assisted approach to make programs
compatible to the relying programming
model~\cite{yaneva-etal-issta2017}; however, \Jbc{Justify they are out
of scope for our subjects...}.

>>>>

\textbf{Usage of massively parallel hardware:}
Previous research investigated the feasibility of testing embedded
software on \emph{Graphics Processing Units} (GPUs) as an alternative
to multicore CPUs~\cite{rajan-etal-ase2014}.
The \emph{Simple Instruction Multiple Data} (SIMD) architecture of
modern GPUs allows running the same test case with different test data
over several threads.
Although benchmarks indicate far superior performance over traditional
multicore CPUs, existing GPU programming-models (\eg,
CUDA~\cite{cuda}, and OpenCL~\cite{opencl}) are compatible only with a
subset of the C/C++ language.
Recent work proposed a compiler-assisted approach to make programs
compatible with the relying programming
model~\cite{yaneva-etal-issta2017}; however, \Jbc{Justify they are out
of scope for our subjects...}.

### 2017-08-30 paper/threats.tex
Removed unnecessary sentence
Moved content about flaky tests from intro to sec III

The main threats to validity of this study are the following.
\textit{External Validity:} Generalization of our findings is limited
to our selection of subjects, testing framework, and build system.  To
mitigate that issue, we selected subjects according to an objective
criteria, described in Section~\ref{sec:subjects}.  It remains to
evaluate the extent to which our observations would change when using
different testing frameworks and build systems.  \textit{Internal
  Validity:} Our results could be influenced by unintentional mistakes
made by humans who interpreted survey data and implemented scripts and
code to collect and analyze data. For example, we developed JUnit
runners to reproduce Maven's parallel configurations and implemented
several scripts to automate our experiments.  All those tasks
could introduce bias in our results.  To mitigate those threats, we
worked in pairs as to increase chances of capturing unintentional
mistakes. Also, we re-executed our experiments on different machines
with different hardware to ensure that our results are consistent.
\textit{Construct Validity:} We considered a number of metrics in this
study that could influence some of our interpretations.  For example,
we measured number of test cases per suite, distribution of test costs
in a suite, time to run a suite, etc.  In principle, these metrics may
not reflect the main problems associated with test
efficiency.
 \Jbc{remember to mention failing tests and how we mitigate
this threat}

>>>>

The main threats to validity of this study are the following.
\textit{External Validity:} Generalization of our findings is limited
to our selection of subjects, testing framework, and build system.  To
mitigate that issue, we selected subjects according to an objective
criteria, described in Section~\ref{sec:subjects}.  It remains to
evaluate the extent to which our observations would change when using
different testing frameworks and build systems.
\textit{Internal Validity:} Our results could be influenced by
unintentional mistakes made by humans who interpreted survey data and
implemented scripts and code to collect and analyze data.
For example, we developed JUnit runners to reproduce Maven's parallel
configurations and implemented several scripts to automate our
experiments (\eg, run tests and detect parallelism enabled by default
in the subjects).
All those tasks could introduce bias in our results.
To mitigate those threats, we worked in pairs as to increase chances
of capturing unintentional mistakes.
\textit{Construct Validity:} We considered a number of metrics in this
study that could influence some of our interpretations.  For example,
we measured number of test cases per suite, distribution of test costs
in a suite, time to run a suite, etc.  In principle, these metrics may
not reflect the main problems associated with test
efficiency.
